Title here

### 2020-09-24 paper/paper.Rmd
change generated points to be grey in tour animation

## Optimisation problem  {#tour-optim}

@@

```{r eval = FALSE}
set.seed(1)
sphere <- geozoo::sphere.hollow(p = 5, n = 1000)$point
path1 <- holes_1d_geo$basis %>% 
  flatten_dbl() %>% matrix(ncol = 5, byrow = TRUE)
path2 <- holes_1d_better$basis %>% 
  flatten_dbl() %>% matrix(ncol = 5, byrow = TRUE)
dt <- rbind(sphere, path1, path2)
colnames(dt) <- c(map_chr(1:5, ~paste0("x", .x)))
pal <- c("#1B9E77","#D95F02","#7570B3", "#E7298A")
color <- c(rep(pal[1], nrow(sphere)),
           rep(pal[2], nrow(path1)),
           rep(pal[3], nrow(path2)))
animate_xy(dt, col = color, cex_slice = 0.8)
animate_slice(dt, col = color)

>>>>

## Optimisation in the tour {#tour-optim}

@@

```{r eval = FALSE}
set.seed(1)
sphere <- geozoo::sphere.hollow(p = 5, n = 1000)$point
path1 <- holes_1d_geo$basis %>% 
  flatten_dbl() %>% matrix(ncol = 5, byrow = TRUE)
path2 <- holes_1d_better$basis %>% 
  flatten_dbl() %>% matrix(ncol = 5, byrow = TRUE)
dt <- rbind(sphere, path1, path2)
colnames(dt) <- c(map_chr(1:5, ~paste0("x", .x)))
pal <- c("#D3D3D3","#D95F02","#7570B3", "#E7298A")
color <- c(rep(pal[1], nrow(sphere)),
           rep(pal[2], nrow(path1)),
           rep(pal[3], nrow(path2)))
cex <- c(rep(1, nrow(sphere)),
         rep(2, nrow(path1)), 
         rep(2, nrow(path2)))
#save_history(animate_xy(dt, col = color, cex = cex))

# save history and play to find the view similar to the PCA view

animate_slice(dt, col = color, pch_other = 20)
